The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-09-14 ecology_and_evolution/paper.Rmd
increased dpi of all images (except one)

# knitr settings
opts_chunk$set(
  # Code output:
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  cache = TRUE,
  # Figure:
  out.width = "100%",
  fig.path = "figures/",
  fig.width = 16 / 2.5,
  fig.height = 9 / 2.5,
  fig.align = "center",
  fig.show = "hold",
  # Etc:
  collapse = TRUE,
  comment = "##",
  tidy.opts = list(width.cutoff = 72),
  tidy = FALSE
)

@@

```{r can-pos-comp-plot, out.width="100%", fig.cap="Posterior distributions of all competition parameters.", echo = FALSE}
autoplot(fit_mod_can_pos, type = "competition")
```

>>>>

# knitr settings
opts_chunk$set(
  # Code output:
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  cache = TRUE,
  # Figure:
  out.width = "100%",
  fig.path = "figures/",
  fig.width = 16 / 2.5,
  fig.height = 9 / 2.5,
  fig.align = "center",
  fig.show = "hold",
  dpi = 600,
  # Etc:
  collapse = TRUE,
  comment = "##",
  tidy.opts = list(width.cutoff = 72),
  tidy = FALSE
)

@@

```{r can-pos-comp-plot, out.width="100%", fig.cap="Posterior distributions of all competition parameters.", echo = FALSE, fig.width = 16 / 2.3}
autoplot(fit_mod_can_pos, type = "competition")
```
